### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex
SYRCoSE: do not mention confusion-free ES

The primitive conflict relation is generated by the $\lfPO$ function.
The two events are considered to be in primitive conflict if they are
not equal and have a common $\lPO$ predecessor. 
For this definition to work properly, we also need 
to assume that each thread has a special initial event 
labelled by a distinguished \emph{thread start} label $\tslab{}$.

@@

Finally, we need a way to reconcile the event structure
with the states of machine's threads. 
To do so we use a function ${\thrdmap : \eventSet \fun \ThrdState}$
which maps an event to a thread state obtained as the result of
the execution of the event's side-effect.

@@

The following theorem asserts that the event structure built this way
indeed satisfies the axioms of the prime confusion free event structure.

\begin{theorem}
  The tuple $\tup{E, \caOrd, \primcfRel}$, where $\caOrd$ and $\primcfRel$
  are defined as described above, forms prime confusion-free event structure.
\end{theorem}

@@

Second, we need to show that the conflict relation defined as 
$ e_1 \primcfRel e_2 \iff e_1 \neq e_2 \wedge \lfPO(e_1) = \lfPO(e2) $
obeys the laws of primitive conflict relation. 
Trivially, this relation is irreflexive, symmetric, and transitive.
Also, it is easy to see that it satisfies choice-locality. 
The side condition $\neg (e_{\lPO} \cfRel e_{\lRF})$ of the rule \ESLoadRule
ensures that the primitive conflict relation would not violate 
hereditary property.

>>>>

We define the conflict relation in two steps. 
First, we define the primitive conflict relation $\primcfRel$ 
which is generated by the $\lfPO$ function.
The two events are considered to be in primitive conflict if they are
not equal and have a common $\lPO$ predecessor. 
For this definition to work properly, we also need 
to assume that each thread has a special initial event 
labelled by a distinguished \emph{thread start} label $\tslab{}$.

@@

Second, we extend the primitive conflict along the causality relation:

$$ e_1 \cfRel e_2 \iff 
   \exists e'_1, e'_2 \in \eventSet \ldotp e'_1 \primcfRel e'_2 \land
   e'_1 \caOrd e_1 \land e'_2 \caOrd e_2 $$

We also need a way to reconcile the event structure
with the states of machine's threads. 
To do so we use a function ${\thrdmap : \eventSet \fun \ThrdState}$
which maps an event to a thread state obtained as the result of
the execution of the event's side-effect.

@@

The following theorem asserts that the event structure built this way
indeed satisfies the axioms of the prime event structure.

\begin{theorem}
  The tuple $\tup{E, \caOrd, \primcfRel}$, where $\caOrd$ and $\primcfRel$
  are defined as described above, forms prime event structure.
\end{theorem}

@@

Second, we need to show that the conflict relation $\cfRel$ defined as 
described above obeys the laws of the conflict relation. 
Trivially, this relation is symmetric, and obeys the hereditary property.
The side condition $\neg (e_{\lPO} \cfRel e_{\lRF})$ of the rule \ESLoadRule
ensures that the conflict relation is irreflexive.
